\thesistitle

### 2019-11-22 pldi/paper.tex
This document needs more code :)

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\noindent type2.cdd\par
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\noindent\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/Users/sbaars/Documents/Kim/jhotdraw"}\par
\noindent\textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6 \textbf{lines}}\par
\noindent\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{SLOC}}\par
\noindent\textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration\par
\noindent\textbf{\textcolor[HTML]{7F0055}{DoNotCompare}} SimpleName, LiteralExpr\par
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

>>>>

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\noindent type2.cdd\par
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\noindent\textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/path/to/java/project"}\par
\noindent\textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{lines}}\par
\noindent\textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{SLOC}}\par
\noindent\textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration\par
\noindent\textbf{\textcolor[HTML]{7F0055}{DoNotCompare}} SimpleName, LiteralExpr\par
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}

\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\noindent type3.cdd\par
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
\noindent \textbf{\textcolor[HTML]{7F0055}{Project}} \textcolor[HTML]{2A00FF}{"/path/to/java/project"}\par
\noindent \textbf{\textcolor[HTML]{7F0055}{Size}} \textcolor[HTML]{7D7D7D}{6} \textbf{\textcolor[HTML]{7F0055}{nodes}}\par
\noindent \textbf{\textcolor[HTML]{7F0055}{Match}} \textbf{\textcolor[HTML]{7F0055}{Subtree}}\par
\noindent \textbf{\textcolor[HTML]{7F0055}{Exclude}} PackageDeclaration, ImportDeclaration\par
\noindent \textbf{\textcolor[HTML]{7F0055}{DoNotCompare}} SimpleName, LiteralExpr\par
\noindent\textbf{\textcolor[HTML]{7F0055}{Compare}} $\ast$  \textbf{\textcolor[HTML]{7F0055}{Subnodes}} Statement \textcolor[HTML]{7D7D7D}{10$\%$}  \textcolor[HTML]{3F7F5F}{/$\ast$  We allow 10$\%$  variance in Statements $\ast$ /}\par
\noindent\makebox[\linewidth]{\rule{\linewidth}{0.4pt}}
